---
title: "Budget Tracker"
format: html
editor: visual
---

# Introduction

This is Quarto file enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>. This document describes how to read in budget data, wrangle the detail, and output it in a more desirable format.

The data utilized to develop this Quarto document is sensitive, so please be aware that references to the data should remain relatively anonymous.

# Initialize Project

## Load packages & functions

```{r}
# packages for data manipulation
library(dplyr)
library(readxl)
library(purrr)
```

## Set parameters

```{r}
dir_path <- paste0("/Users/", Sys.info()["user"], "/Software/Git Local/budget-consolidation/")
eventfiles <- list.files("DATA", pattern="Events", full.names = TRUE)
plfiles <- list.files("DATA", pattern="Profit-Loss", full.names = TRUE)
```

## Read data

```{r}
events <- map(eventfiles, read_xls)
profit_loss <- map(plfiles, read_xls)
```

# Clean Data

## Bind dataframes

```{r}
profit_loss_df <- bind_rows(profit_loss, .id = "column_label")
events_df <- bind_rows(events, .id = "column_label")
```
